A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-06-13 paper/paper.tex
Unifying a bit the presentation between the main part and the appendix

In the total resolution experiment, we observed similar results as in the experiment on the Rome graphs for small graphs, that is, our unrestricted algorithm outperforms the other three ones, while the restricted variant of our algorithm yields drawings and then the algorithm by Argyriou et al.; see Fig.~\ref{fig:northTotal-1}. For larger graphs, however, these three algorithms achieve similar results while still outperforming the algorithm by Huang et al. The results for the aspect ratio and number of crossings are similar to those of the crossing resolution experiment, with the exception of the fact that the algorithm of Huang et al. performs more stable with respect to the aspect ratio; see Figs.~\ref{fig:northTotal-2} and~\ref{fig:northTotal-3}. With respect to the number of iterations our two algorithms and the one by Argyriou et al. show similar behaviour needing more iterations than the algorithm by Huang et al.; see Fig.~\ref{fig:northTotal-4}. Observe that the number of iterations does not seem to correlate with the number of vertices.

>>>>

In the total resolution experiment, we observed similar results as in the experiment on the Rome graphs for small graphs, that is, our unrestricted algorithm outperforms the other three ones, while the restricted variant of our algorithm yields drawings and then the algorithm by Argyriou et al.; see Fig.~\ref{fig:northTotal-1}. For larger graphs, however, these three algorithms achieve similar results while still outperforming the algorithm by Huang et al. The results for the aspect ratio and number of crossings are similar to those of the crossing resolution experiment, with the exception of the fact that the algorithm of Huang et al. performs more stable with respect to the aspect ratio; see Figs.~\ref{fig:northTotal-2} and~\ref{fig:northTotal-3}. With respect to the number of iterations, our two algorithms and the one by Argyriou et al. show similar behavior needing more iterations than the algorithm by Huang et al.\ in order to converge; see Fig.~\ref{fig:northTotal-4}. %Observe that the number of iterations does not seem to correlate with the number of vertices.
